Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-23 Thesis/01-chap1.Rmd
finish heter

Lemma \@ref(lemma:heter) shows that variance and covariance of the residuals depend on $\boldsymbol{X}$. We could plot the one standard deviation around the residuals to indicate the region about 68% of the residuals should landed. Figure \@ref(fig:hetershape) illustrates different shapes of residuals with various values of $a$ and $b$. From the plot, it can be observed that if $a = 0$, the residual plot looks like the shape of butterfly. If $a = \pm 1$, it looks like a triangle, and the sign of $a$ determines the direction of the shape. Parameter $b$ is controlling the strength of the signal. As $b$ increases, the pattern becomes less noisy.

@@

@@

>>>>

Lemma \@ref(lemma:heter) shows that variance and covariance of the residuals depend on $\boldsymbol{X}$. We could plot the one standard deviation around the residuals to indicate the region about 68% of the residuals should landed on. Figure \@ref(fig:hetershape) illustrates different shapes of residuals undder various values of $a$ and $b$. From the plot, it can be observed that if $a = 0$, the residual plot looks like the shape of butterfly. If $a = \pm 1$, it looks like a triangle, and the sign of $a$ determines the direction of the shape. Parameter $b$ is controlling the strength of the signal. As $b$ increases, the pattern becomes less noisy.

@@

For the heteroskedasticity model, the conventional test we used was Breusch–Pagan test [@breusch_simple_1979], which tested whether the variance of the error terms of the regression is dependent on the regressors. @majumder_validation_2013 suggested that visual test is not expected to perform equally well as conventional test especially when there exists a exact conventional test. However, in contrast to the F-test used in the cubic model, Breusch–Pagan test is an approximate test. Thus, the power of visual test may exceed the power of Breusch–Pagan test. Throughout the study, Breusch–Pagan test statistic and p-value were recorded for comparison.

@@

The model definitions given in the previous two sections does not include the specification of the regressors. In this sections, distribution of $\boldsymbol{X}$ and $\boldsymbol{Z}$ will be discussed.

The cubic model involves the use of both $\boldsymbol{X}$ and $\boldsymbol{Z}$. In the simulation, $X_i$, $i=1,...,n$, had equal chance to follow one of the following distributions: $N(0, 0.09)$, $U(-1, 1)$, $Lognormal(0,0.36)$ and $-Lognormal(0,0.36)$.

Normal and uniform distributions are

### 2022-02-23 Thesis/_book/thesis.tex
finish heter

Lemma \ref{lemma:heter} shows that variance and covariance of the residuals depend on \(\boldsymbol{X}\). We could plot the one standard deviation around the residuals to indicate the region about 68\% of the residuals should landed. Figure \ref{fig:hetershape} illustrates different shapes of residuals with various values of \(a\) and \(b\). From the plot, it can be observed that if \(a = 0\), the residual plot looks like the shape of butterfly. If \(a = \pm 1\), it looks like a triangle, and the sign of \(a\) determines the direction of the shape. Parameter \(b\) is controlling the strength of the signal. As \(b\) increases, the pattern becomes less noisy.

@@

@@

>>>>

Lemma \ref{lemma:heter} shows that variance and covariance of the residuals depend on \(\boldsymbol{X}\). We could plot the one standard deviation around the residuals to indicate the region about 68\% of the residuals should landed on. Figure \ref{fig:hetershape} illustrates different shapes of residuals undder various values of \(a\) and \(b\). From the plot, it can be observed that if \(a = 0\), the residual plot looks like the shape of butterfly. If \(a = \pm 1\), it looks like a triangle, and the sign of \(a\) determines the direction of the shape. Parameter \(b\) is controlling the strength of the signal. As \(b\) increases, the pattern becomes less noisy.

@@

For the heteroskedasticity model, the conventional test we used was Breusch--Pagan test \autocite{breusch_simple_1979}, which tested whether the variance of the error terms of the regression is dependent on the regressors. \textcite{majumder_validation_2013} suggested that visual test is not expected to perform equally well as conventional test especially when there exists a exact conventional test. However, in contrast to the F-test used in the cubic model, Breusch--Pagan test is an approximate test. Thus, the power of visual test may exceed the power of Breusch--Pagan test. Throughout the study, Breusch--Pagan test statistic and p-value were recorded for comparison.

@@

The model definitions given in the previous two sections does not include the specification of the regressors. In this sections, distribution of \(\boldsymbol{X}\) and \(\boldsymbol{Z}\) will be discussed.

The cubic model involves the use of both \(\boldsymbol{X}\) and \(\boldsymbol{Z}\). In the simulation, \(X_i\), \(i=1,...,n\), had equal chance to follow one of the following distributions: \(N(0, 0.09)\), \(U(-1, 1)\), \(Lognormal(0,0.36)\) and \(-Lognormal(0,0.36)\).

Normal and uniform distributions are
